The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-09-28 manuscript.Rmd
number supplementary figures correctly
improve rank abundance plots

## Supplementary material

@@

```{r rank-abundance, fig.cap="Rank abundance plots for most represented phyla."}
knitr::include_graphics("figures/rank_abundance.pdf")
```

>>>>

# Supplementary material

\renewcommand{\thefigure}{S\arabic{figure}}

\setcounter{figure}{0}

@@

```{r rank-abundance, fig.cap="Rank abundance plots for most represented phyla based on the number of samples (A), and the number of cells occupied in map of Fig. \\@ref(fig:map-diversity-sampling) (B)"}
knitr::include_graphics("figures/plot_rank_abundance.pdf")
```

* list of marine invertebrate species from the continental USA: `list_species_us.csv`
* list of marine invertebrate species from the Gulf of Mexico: `list_species_gom.csv`
* list of marine invertebrate species from the Pacific Northwest: `list_species_pnw.csv`
